---
title: "Using R to Orchestrate APIs -- Demonstration"
author: "John Little"
date: '`r Sys.Date()`'
output:
  html_notebook: default
---

## Demonstration

### To Follow Along

- Open the Web Page - http://libjohn.github.io/rcs2017/demonstration.nb.html

**OR**

1. Open the Notebook in an RStudio Docker Container - https://vm-manage.oit.duke.edu/containers/rstudio 
2. Project > New Project
3. Version Contrl > Git 
4. Repository URL = https://github.com/libjohn/r-api-json.git > Create Project 
5. Open *demonstration.Rmd* file
    + Run All

--- 

### Overview of OMDB api 

- http://www.omdb.org/
    - like http://imdb.com/
    - no API keys requried
    - **The API** http://www.omdbapi.com/

--- 

### Demonstration

```{r load-library-package}
# https://cran.r-project.org/web/packages/jsonlite/vignettes/json-aaquickstart.html
library(jsonlite)
```


### Single JSON array
When the server response is a single JSON array, JSONlite makes viewing the data pretty simple.
```{r singleJSONresult}
oneJSONresult <- fromJSON("http://www.omdbapi.com/?t=rocky&y=&plot=full&r=json")
```

---

```{r}
oneJSONresult
```


--- 

##### The vector object behaves as you would expect in R.  

- You can list all the variable names.

```{r}
names(oneJSONresult)
```

- List an individual element

```{r}
oneJSONresult$Title
```

```{r}
oneJSONresult$Awards
```


---

### A JSON List
The **results of this code-snippet react differently** between the *console*, the *Notebook script* (console), and the *Notebook HTML* output.  In the script-output you can find the object names of the list, in this case dollar-search: `$Search`.  Or, you can use bracket notation: `[[1]]`.  Once you identify the object name, it's easier to identify the vector names within the `$Search` data frame.
```{r}
jsonSeriesResutlsList <- fromJSON("http://www.omdbapi.com/?s=rocky&type=series&r=json&page=1")
jsonSeriesResutlsList

```

---  

#### Search results of the JSON list as a data frame.
```{r}
jsonSeriesResutlsList$Search
```

--- 

#### Title Vector of the Search Data Frame 
```{r}
jsonSeriesResutlsList$Search$Title
```

---

## Next

- [Handson.Rmd](http://libjohn.github.io/rcs2017/handson.nb.html)
