---
title: "httR packages, searching the API at OMDB.com"
output:
  html_notebook: httR-OMDB.nb.html
---

```{r load-library-package}
library(httr)  
# https://cran.r-project.org/web/packages/httr/vignettes/quickstart.html
# https://www.rstudio.com/resources/webinars/extracting-data-from-the-web-part-1/
```

## Use httR to GET data
The goal is to  scrape the data from the OMDB.com [API](http://www.omdbapi.com).  Notice that using the GET verb (brokered by the httR packge) yields a webserver response.  In later sections we use the `httr::content()` function to access the rest of the data returned in this request.  But first, you may want to familiarize yourself with the standard [JSON](https://en.wikipedia.org/wiki/JSON) response following the client GET request.  You may also fine it useful to paste (and format) the JSON using a separate [JSON viewer](http://jsonviewer.stack.hu/).  The JSON viewer can help clarify the key-value nature and content of the response which you will put to use as you parse your data.

* [url0](http://www.omdbapi.com/?t=rocky&y=&plot=full&r=json)  
* [url1](http://www.omdbapi.com/?s=rocky&type=series&r=json&page=1)   
* [url2](http://www.omdbapi.com/?s=rocky&type=series&r=json&page=2)  
```{r get URLs}
# get a single movie by title
# API documentation for string/search contruction:  https://www.omdbapi.com/
url0 <- GET("http://www.omdbapi.com/?t=rocky&y=&plot=full&r=json")
url0

url1 <- GET("http://www.omdbapi.com/?s=rocky&type=series&r=json&page=1")

url2 <- GET("http://www.omdbapi.com/?s=rocky&type=series&r=json&page=2")
```

## httR can parse 
In this case, parse the JSON results with `httr::str()`.  Note that the structure (`str()`) of the response gives a very nice [R] view of a the JSON key-value pairs.
```{r preview-results}
str(content(url0))
```

To see the escaped *text* of the response
```{r content-asText}
content(url0, "text")
```

Or you can parse the response into a list
```{r content-parsed}
content(url0, "parse")
```

Which then allows you to easily access the elements of the list.
```{r sub-elements-ofContent}

# content(url0, "parse")$Title
info <- content(url0, "parse")
# info$Plot
info$Awards

```

That's a pretty convenient way to access the individual elements of a relatively simple JSON resopnse.  But JSON can contain embeded hierarchies of key-value pairs, as is the case when the search results return a result consisting of twenty separate titles.
```{r series}
# url1 = http://www.omdbapi.com/?s=rocky&type=series&r=json&page=1
series <- content(url1, "parse")
series
```


The OMDB-API response puts a JSON array inside an overall JSON wrapper, an array of arrays.  This makes accessing the individual data a bit more opaque.
```{r arrayOfArray}

# Take the first element of the second componenet of the array response
series$Search[[2]][1]

# That first element is $Title, of the second componenet of the array response labeled as $Search
series$Search[[2]]$Title
```
