---
title: "JSONlite packages, searching the API at OMDB.com"
output:
  html_notebook: default
---

```{r load-library-package}
#library(rvest)  
library(jsonlite)
# https://cran.r-project.org/web/packages/jsonlite/vignettes/json-aaquickstart.html

# for building tibbles
library(tidyverse)
```

## JSONlite

### Single JSON array
When the server response is a single JSON array, JSONlite makes viewing the data pretty simple.  (This list response is equivalent to `httr::content(url, "parse")`
```{r singleJSONresult}
oneJSONresult <- fromJSON("http://www.omdbapi.com/?t=rocky&y=&plot=full&r=json")
oneJSONresult
```

It's also easy to gather a single element fromthe response
```{r}
oneJSONresult$Title
```


### A JSON Matrix
The **results of this code-snippet reacts differently** between the *console*, the *Notebook script* (console), and the *Notebook HTML* output.  In the Notebook script-output you can find the component name, in this case dollar-search: `$Search`.  Or, you can use bracket notation: `[[1]]`.  Once you identify the component name, it's easier to identify the element names.
```{r}
jsonSeriesResutlsMatrix <- fromJSON("http://www.omdbapi.com/?s=rocky&type=series&r=json&page=1")
jsonSeriesResutlsMatrix
```

### Call the search results and coerce the JSON array into a data frame.
```{r}
jsonSeriesResutlsMatrix$Search
```


## Nothing below this header needs to be included in a demo about JSONlite.

### Handling all the elements in the components.  
i.e. gather the series IDs from the  JSON matrix.  
```{r series-id}
jsonSeriesResutlsMatrix[[1]]$imdbID
jsonSeriesResutlsMatrix$Search$imdbID

```

## Gather information on each title in the series result-set
Use imdbID to search the API
```{r}
baseURL <- ("http://www.omdbapi.com/?plot=short&r=json&")
queryArraybyIMDBid <- paste0(baseURL, "i=", jsonSeriesResutlsMatrix$Search$imdbID)

```


```{r}
queryArraybyIMDBid
```




## Individual Movie Title Results
Query result from the 2nd component of the array result
```{r}
fromJSON(queryArraybyIMDBid[[1]])
```


```{r}
# clear vector
rm(title, yr, release, imdbID, rating, votes)

title <- fromJSON(queryArraybyIMDBid[[1]])$Title
type <- fromJSON(queryArraybyIMDBid[[1]])$Type
yr <- fromJSON(queryArraybyIMDBid[[1]])$Year
release <- fromJSON(queryArraybyIMDBid[[1]])$Released
imdbID <- fromJSON(queryArraybyIMDBid[[1]])$imdbID
rating <- fromJSON(queryArraybyIMDBid[[1]])$imdbRating
votes <- fromJSON(queryArraybyIMDBid[[1]])$imdbVotes

for (i in 2:length(queryArraybyIMDBid)) {  
  title <- append(title, fromJSON(queryArraybyIMDBid[[i]])$Title)
  type <- append(type, fromJSON(queryArraybyIMDBid[[i]])$Type)
  yr <- append(yr, fromJSON(queryArraybyIMDBid[[i]])$Year)
  release <- append(release, fromJSON(queryArraybyIMDBid[[i]])$Released)
  imdbID <- append(imdbID, fromJSON(queryArraybyIMDBid[[i]])$imdbID)
  rating <- append(rating, fromJSON(queryArraybyIMDBid[[i]])$imdbRating)
  votes <- append(votes, fromJSON(queryArraybyIMDBid[[i]])$imdbVotes)
}

omdb_df <-  data_frame(
  title = title[1:10], 
  type = type[1:10],
  year = yr[1:10], 
  release = release[1:10], 
  imdbID=imdbID[1:10], 
  rating = as.numeric(rating[1:10]), 
  votes = as.numeric(votes[1:10])
)

omdb_df

# try add_row()
```

```{r}


omdb_df2 <-  data_frame(
title = fromJSON(queryArraybyIMDBid[[1]])$Title,
type = fromJSON(queryArraybyIMDBid[[1]])$Type,
yr = fromJSON(queryArraybyIMDBid[[1]])$Year,
release = fromJSON(queryArraybyIMDBid[[1]])$Released,
imdbID = fromJSON(queryArraybyIMDBid[[1]])$imdbID,
rating = fromJSON(queryArraybyIMDBid[[1]])$imdbRating,
votes = fromJSON(queryArraybyIMDBid[[1]])$imdbVotes
)

omdb_df2



for (i in 2:length(queryArraybyIMDBid)) {
  omdb_df2 <- omdb_df2 %>% 
    add_row(title = fromJSON(queryArraybyIMDBid[[i]])$Title, 
            type = fromJSON(queryArraybyIMDBid[[i]])$Type, 
            yr = fromJSON(queryArraybyIMDBid[[i]])$Year, 
            release = fromJSON(queryArraybyIMDBid[[i]])$Released,
            imdbID = fromJSON(queryArraybyIMDBid[[i]])$imdbID, 
            rating = fromJSON(queryArraybyIMDBid[[i]])$imdbRating, 
            votes = fromJSON(queryArraybyIMDBid[[i]])$imdbVotes)
}

omdb_df2
#rm(omdb_df2)

```


